HSF Community White Paper on Data Organization, Management and Access (DOMA)

### 2018-03-21 CWP/papers/HSF-CWP-2017-04_doma/latex/hsf-cwp-dm.tex
DOMA CWP: add author list
DOMA CWP: fix roadmap formatting

Authors: D. Berzano, R.M. Bianchi, I. Bird, B. Bockelman, K. De, S.
Campana, D. Duellmann, P.Elmer, R. Gardner, V. Garonne, C. Grandi, O.
Gutsche, A. Hanushevsky, B. Holzman, B. Jayatilaka, I. Jimenez, M.
Jouvin, O. Keeble, A. Klimentov, V. Kuznetsov, E. Lançon, M. Lassnig, T.
Malik, C. Maltzahn, S. McKee, D. Menasce, M. Livny, B. Nitzberg, A.
Norman, J. Pivarski, M. Schulz, H. Severini, M. Sevilla, L.
Sexton-Kennedy, E. Vaandering, N. Watkins, T. Wenaus, F. Wuerthwein

@@

\protect\hypertarget{_y0jes1qd33m1}{}{}Event-based granularity - Can
this be implemented efficiently, scalably and in a cost-effective manner
for relevant use cases (reco, simulation, event-picking)? Does it
provide an advantage over current file-based granularity?

@@

\protect\hypertarget{_txtjm296wo2a}{}{}Data organization and analysis
technologies - How can we benefit from technologies adopted by the
big-data world?

@@

\protect\hypertarget{_49uk6huxen3e}{}{}Data caching - What role will
caching play to use compute resources and what technologies will be
used?

@@

\protect\hypertarget{_rjxbgr6m4duh}{}{}Getting the most out of the
storage diversity - how to minimize HEP infrastructure cost by
exploiting varied quality of service from different storage
technologies?

@@

\protect\hypertarget{_kixm6ns2odgg}{}{}Efficiency / latency (global
optimization) - Can we globally optimize data access latency vs
efficiency of CPU use at a sustainable cost?

>>>>

\input{authors.tex}

@@

\subsection{Event-based granularity}\label{event-based-granularity}
Can this be implemented efficiently, scalably and in a cost-effective manner
for relevant use cases (reco, simulation, event-picking)? Does it
provide an advantage over current file-based granularity?

@@

\subsection{Data organization and analysis
technologies}\label{data-organization-and-analysis}
How can we benefit from technologies adopted by the
big-data world?

@@

\subsection{Data caching}\label{data-caching}
What role will
caching play to use compute resources and what technologies will be
used?

@@

\subsection{Getting the most out of the
storage diversity}\label{storage-diversity}
how to minimize HEP infrastructure cost by
exploiting varied quality of service from different storage
technologies?

@@

\subsection{Efficiency / latency (global
optimization}\label{efficiency-latency}
Can we globally optimize data access latency vs
efficiency of CPU use at a sustainable cost?
